---
title: "Analysis"
author: "Jiayu Li"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::readthedown:
    toc_depth: 3
    # toc_float:
    #   collapsed: FALSE
    code_folding: hide
    # default_style: "light"
    # downcute_theme: "chaos"
    css: custom_wide_only.css
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read data, include=FALSE}
# source("R/funcitons.R")
library(magrittr)
library(data.table)
library(lubridate)
library(plotly)
library(DT)
library(shiny)
library(ggplot2)
library(janitor)
library(here)

dt_innova <- fread(here("clean_data_5_min/innova/dt_innova.csv"))
dt_velocicalc <- fread(here("clean_data_5_min/velocicalc/dt_velocicalc.csv"))
dt_wind_sensor <- fread(here("clean_data_5_min/wind_sensor/dt_wind_sensor.csv"))

dt_innova <- dt_innova[!( datetime >= ymd_hm("2023-05-04 12:40") & datetime <= ymd_hm("2023-05-04 14:05") & innova_ch == 5)]

# dt_innova[datetime >= ymd_hm("2023-05-04 12:40") & datetime <= ymd_hm("2023-05-04 14:05")]
```

```{r themes, include=FALSE}

s_r_loc_colors <- c(
  "Receptor room"   = "#8dd3c7",
  "Receptor window" = "#b3de69",
  "Source room"     = "#fb8072",
  "Source window"   = "#fdb462",
  "Room aside the source" = "#bebada",
  "Downstair" = "#d9d9d9"
)

nea_colors <- c("#BED73B","#58B6DC", "#F58A06","#bebada")

library(RColorBrewer)

# nea_colors <- brewer.pal(n = 6, name = "Accent")

```


```{r read condition files, echo=FALSE}
cond_general_scenario <- fread(here("clean_data/conditions/general_scenario.csv"))
cond_innova_vc <- fread(here("clean_data/conditions/innova_vc.csv"))
cond_source_and_receptor <- fread(here("clean_data/conditions/source_and_receptor.csv"))
cond_wind_sensor <- fread(here("clean_data/conditions/wind_sensor.csv"))

# cond_general_scenario[, start_datetime := dmy_hm(paste(exp_date, start_time) ) - hours(8)]
# cond_general_scenario[, end_datetime := dmy_hm(paste(exp_date, end_time) )- hours(8)]

cond_general_scenario[, start_datetime := dmy_hm(paste(exp_date, start_time) ) ]
cond_general_scenario[, end_datetime := dmy_hm(paste(exp_date, end_time) ) ]
```

# Conditions

```{r echo=FALSE, message=FALSE, warning=FALSE}

cond_general_scenario[, note := iconv(note, to = "utf-8")]

copy(cond_general_scenario)  %>%

  .[, start_datetime := start_datetime - hours(8)] %>%  # this is only correcting the error in the table display

   .[, end_datetime := end_datetime - hours(8)] %>%  # this is only correcting the error in the table display
  .[,-c("exp_id", "test_id", "start_datetime", "end_datetime")] %>%
  datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) #%>% formatDate(c("start_datetime","end_datetime"), method = "toLocaleString")

```


```{r add conditions general, echo=TRUE}
add_general_condition <- function(dt, dt_condi) {
  for (i in 1:length(dt_condi$start_datetime) ) {
    dt[datetime >= dt_condi$start_datetime[i] & datetime <= dt_condi$end_datetime[i],
       `:=`(test_id = dt_condi$test_id[i],
            exp_id = dt_condi$exp_id[i],
            sf6_rate = dt_condi$sf6_rate[i],
            building_type = dt_condi$building_type[i],
            scenario = dt_condi$scenario[i],
            test_type = dt_condi$test_type[i],
            receptor_door = dt_condi$receptor_door[i]
            )]
  }
}

add_general_condition(dt_velocicalc, cond_general_scenario)
add_general_condition(dt_innova, cond_general_scenario)
add_general_condition(dt_wind_sensor, cond_general_scenario)
```


## Innova conditions

```{r echo=FALSE, message=FALSE, warning=FALSE}

    cond_innova_vc %>%

  datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))

```


```{r add conditions innova, echo=TRUE}
dt_innova <- cond_source_and_receptor[cond_innova_vc,
                                      on = .(test_id, s_r)][dt_innova,
                                                            on = .(test_id, innova_ch)] %>%
  .[!is.na(test_id)]
```



## Source and receptor conditions

```{r echo=FALSE, message=FALSE, warning=FALSE}

    cond_source_and_receptor%>%

  datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))

```

```{r add conditions velocicalc, echo=TRUE}
dt_velocicalc %>% setnames(old = "equip_unit", new = "vc_unit")

dt_velocicalc <- cond_source_and_receptor[cond_innova_vc,
                                          on = .(test_id, s_r)][vc_unit != ""][dt_velocicalc[, `:=`(loc = NULL,
                                                                                                    s_r = NULL)], on =
                                                                                 .(test_id, vc_unit)] %>%
  .[!is.na(test_id)]
```


## Wind sensor conditions

```{r echo=FALSE, message=FALSE, warning=FALSE}

    cond_wind_sensor %>%

  datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))

```

### Calculate `u`, `v`, and `w` (need double-check)

(Please check if my understanding is correct or not.)

`u` and `v` use the data from the sensors marked "h", and `w` uses the data from the sensors marked "v". The equations for calculation `u`, `v`, and `w` are as follows. 

$$
u = WIMWV_{<3>} * \sin(\frac{WIMWV_{<1>} * \pi}{180})
$$ 
$$
v = WIMWV_{<3>} * \cos(\frac{WIMWV_{<1>} * \pi}{180})
$$ 
$$
w = -WIMWV_{<3>} * \cos(\frac{WIMWV_{<1>} * \pi}{180})
$$

```{r add conditions, echo=TRUE}

dt_wind_sensor_ws_wd <- cond_source_and_receptor[cond_wind_sensor,
                                           on = .(test_id, s_r, room_type)][dt_wind_sensor,
                                                                            on = .(test_id, wind_sensor_unit)] #%>%
  # .[!is.na(test_id)]

# dt_wind_sensor_ws_wd[position == "h", u := vel_mag_WIMWV_3 * sin(vel_angle_WIMWV_1 * pi/180)]

dt_wind_sensor_ws_wd[position == "h", u_from_hori_sensor := vel_mag_WIMWV_3 * sin(vel_angle_WIMWV_1 * pi/180)]
dt_wind_sensor_ws_wd[position == "v", u_from_verti_sensor := vel_mag_WIMWV_3 * sin(vel_angle_WIMWV_1 * pi/180)]

dt_wind_sensor_ws_wd[position == "h", v := vel_mag_WIMWV_3 * cos(vel_angle_WIMWV_1 * pi/180)]
dt_wind_sensor_ws_wd[position == "v", w := - vel_mag_WIMWV_3 * cos(vel_angle_WIMWV_1 * pi/180)]

# correct test_id == 9 that "the MARKER was facing to outside of the room."
# dt_wind_sensor_ws_wd[test_id == 9, u := -u]
dt_wind_sensor_ws_wd[test_id == 9, u_from_hori_sensor := -u_from_hori_sensor]
dt_wind_sensor_ws_wd[test_id == 9, v := -v]


cols <- names(dt_wind_sensor_ws_wd)[c(1:9, 12:14,21:26)]

dt_wind_sensor <- dt_wind_sensor_ws_wd[, lapply (.SD, mean, na.rm = T), .SDcols = c(
    # "u",
    "u_from_hori_sensor",
    "u_from_verti_sensor",
    "v",
    "w"
  ), by = cols]

```

<!-- # Raw data -->

<!-- Please note that the `experimental ID` is relabeled according to the condition table (the `exp_id` column) in [this link](https://jiayuliaq.shinyapps.io/check_raw_data_shiny/). Among `r max(cond_general_scenario$exp_id)` `experimental IP`, some are real experimental "test", some are "ACH" decay test, and others are "trail" or "invalid" as labeled as `Test type` in the plot title. -->

# Raw data

## Innova

```{r echo=FALSE, out.width='100%', out.height='100%'}
df <- dt_innova[, date := date(datetime)]

ui_1 <- fluidPage(
  fluidRow(
    column(3,
  # selectInput('exp_id', 'Select experiment ID', choices = sort(unique(df$exp_id)), selected = 13),
  dateInput(
    'date',
    'Select Date',
    value = max(df$date),
    min = min(df$date),
    max = max(df$date),
    datesdisabled = setdiff(seq.Date(min(df$date), max(df$date), by = "day"), df$date %>% unique) %>% as_date
    ),
  checkboxInput('log', 'Logarithmic Scale', FALSE) 
  ),
  column(3,
  selectInput('variable', 'Select Parameter', c('sf6_conc'))
  )
)
,
fluidRow(column(12,
                mainPanel(
                  plotlyOutput("timeseriesPlot")
                ))))

# Define server logic for timeseries plot
server_1 <- function(input, output) {
  output$timeseriesPlot <- renderPlotly({

    # filteredData <- copy(df)[exp_id == input$exp_id]
    filteredData <- copy(df)[date == input$date]
    
    filteredData[s_r == "s", s_r := "Source"]
    filteredData[s_r == "r", s_r := "Receptor"]
    
    filteredData[, type_ := paste(s_r, loc)]
    
    filteredData[type_ %like% "downstair", type_ :="Downstair"]
    filteredData[type_ %like% "room_aside", type_ :="Room aside the source"]
    
    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ get(input$variable),
      color = ~ type_,
      type = 'scatter',
      mode = 'lines',
      colors = s_r_loc_colors
      
    ) %>%
      layout(
        title = NULL,
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable,
          type = ifelse(input$log, "log", "linear")
        ),
        legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.5,
                     y = 1.1),
        # autosize = F, 
        width = 750, height = 500
      )
  })
}

# Run the app
shinyApp(ui = ui_1, server = server_1, options = list(height = 650) )
```


## VelociCalc

```{r echo=FALSE}
df_2 <- dt_velocicalc[, date := date(datetime)]

ui_1 <- fluidPage(
  fluidRow(
    column(3,
      dateInput(
      'date',
      'Select Date',
      value = max(df_2$date),
      min = min(df_2$date),
      max = max(df_2$date),
      datesdisabled = setdiff(seq.Date(min(df_2$date), max(df_2$date), by = "day"), df_2$date %>% unique) %>% as_date
    )
    ),
    column(3,
      selectInput('variable', 'Select Parameter', c('vel','temp',"rh"))
    ),
),
  fluidRow(
    column(12,
    mainPanel(
      plotlyOutput("timeseriesPlot")
    )
    )
  )
)

# Define server logic for timeseries plot
server_1 <- function(input, output) {
  output$timeseriesPlot <- renderPlotly({

    filteredData <- copy(df_2)[date == input$date]
    
    filteredData[s_r == "s", s_r := "Source"]
    filteredData[s_r == "r", s_r := "Receptor"]
    
    filteredData[, type_ := paste(s_r, loc)]
    
    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ get(input$variable),
      color = ~ type_,
      type = 'scatter',
      mode = 'lines',
      colors = s_r_loc_colors
    ) %>%
      layout(
        title = NULL#,"\n", 
          # "Receptor door: ", filteredData$receptor_door %>% unique ,"\n", 
          # "Building type: ", filteredData$building_type %>% unique
          ,
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable
        ),
        legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.5,
                     y = 1.1),
        # autosize = F, 
        width = 750, height = 500
      )
  })
}

# Run the app
shinyApp(ui = ui_1, server = server_1, options = list(height = 650) )
```


## Wind sensor

### Line plots
```{r echo=FALSE}
df_3 <- dt_wind_sensor[, date := date(datetime)]

ui_1 <- fluidPage(
  fluidRow(column(3,
      dateInput(
      'date',
      'Select Date',
      value = max(df_3$date),
      min = min(df_3$date),
      max = max(df_3$date),
      datesdisabled = setdiff(seq.Date(min(df_3$date), max(df_3$date), by = "day"), df_3$date %>% unique) %>% as_date
    ) ),
    column(3,
           selectInput('variable', 'Select Parameter', c(#'u',
                                                         'u_from_hori_sensor',
                                                         'u_from_verti_sensor',
                                                         "v",
                                                         "w")))), 
 fluidRow(column(12,
    mainPanel(
      plotlyOutput("timeseriesPlot")
    )
 ))
)

# Define server logic for timeseries plot
server_1 <- function(input, output) {
  output$timeseriesPlot <- renderPlotly({

    filteredData <- copy(df_3)[date == input$date]
    
    filteredData[s_r == "s", s_r := "Source"]
    filteredData[s_r == "r", s_r := "Receptor"]
    
    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ get(input$variable),
      color = ~ paste(s_r, loc, room_type),
      type = 'scatter',
      mode = 'lines'
    ) %>%
      layout(
        title = NULL#,"\n", 
          # "Receptor door: ", filteredData$receptor_door %>% unique ,"\n", 
          # "Building type: ", filteredData$building_type %>% unique
          ,
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable
        ),
        width = 750, height = 500,
        legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.5,
                     y = 1.1)
      )
  })
}

# Run the app
shinyApp(ui = ui_1, server = server_1, options = list(height = 650) )
```

### Wind rose plots

All the calculationa and plots are based on the data from the `$WIMWV` section.

```{r wind rose, echo=FALSE}
library(openair)
dt_wind_sensor_ws_wd[, date := date(datetime)]

# dt_wind_sensor_ws_wd[, datetime := datetime - hours(8)]
ui_4 <- fluidPage(
  fluidPage(column(3,
    # selectInput('exp_id', 'Select experiment ID', choices = sort(unique(dt_wind_sensor_ws_wd$exp_id)), selected = 13),
    dateInput(
      'date',
      'Select Date',
      value = max(dt_wind_sensor_ws_wd$date),
      min = min(dt_wind_sensor_ws_wd$date),
      max = max(dt_wind_sensor_ws_wd$date),
      datesdisabled = setdiff(seq.Date(min(dt_wind_sensor_ws_wd$date), max(dt_wind_sensor_ws_wd$date), by = "day"), dt_wind_sensor_ws_wd$date %>% unique) %>% as_date
    )),
    column(9,
    sliderInput(
      "timeRange",
      label = "Select Time Range",
      min = as.POSIXct("9:00:00", format = "%H:%M:%S", tz = "Singapore"),
      max = as.POSIXct("22:00:00", format = "%H:%M:%S", tz = "Singapore"),
      value = c(
        as.POSIXct("13:00:00", format = "%H:%M:%S", tz = "Singapore"),
        as.POSIXct("14:00:00", format = "%H:%M:%S", tz = "Singapore")
      ),
      timeFormat = "%H:%M:%S"
    )
  )),
  fluidPage(column(12,
  mainPanel(plotOutput("timeseriesPlot", width = 700))
  ))
)

# Define server logic for timeseries plot
server_4 <- function(input, output) {
    
  
  output$timeseriesPlot <- renderPlot({

filteredData_1 <- copy(dt_wind_sensor_ws_wd)[position == "h" &
                                       date(datetime) == ymd(input$date) ]
filteredData  <-  
  filteredData_1[hour(datetime) * 60 + minute(datetime) >= hour(input$timeRange[1]) * 60 + minute(input$timeRange[1]) + 8*60] %>%
  .[hour(datetime) * 60 + minute(datetime) <= hour(input$timeRange[2]) * 60 + minute(input$timeRange[2]) + 8*60]

filteredData[, type_ := room_type]
filteredData[s_r == "s", type_ := paste(room_type, "Source")]
filteredData[s_r == "r", type_ := paste(room_type, "Receptor")]


windRose(
  mydata = filteredData,
  ws = "vel_mag_WIMWV_3",
  wd = "vel_angle_WIMWV_1",
  type = "type_",
  breaks = c(0, 0.5, 1, 1.5, 2, 4),
  paddle = F,
  main = paste("For the selected date, please only select time between:",  format(min(filteredData_1$datetime), format = "%H:%M:%S"), "and", format(max(filteredData_1$datetime), format = "%H:%M:%S"))
)

# filteredData %>% ggplot() + geom_line(aes(datetime, vel_mag_WIMWV_3, color = type_))
  })
}

# Run the app
shinyApp(ui = ui_4, server = server_4, options = list(height = 500) )

```


# Preliminary results


## `Receptor room` upon `source room` ratio 

### Fixed scale (at 1%)

```{r echo=FALSE, fig.height=5, fig.width=8, warning=FALSE}
dt_innova[hour(datetime) %in% c(12:14), dn := "Daytime"]
dt_innova[hour(datetime) %in% c(18:20), dn := "Nighttime"]

dt_innova %>% setorder(datetime)
dt_innova[, time_index := seq.int(1:.N), by = .(exp_id, innova_ch)]

p <- dt_innova[test_type == "Test" & loc == "room" & time_index > 4 ] %>%
  dcast(datetime + building_type + receptor_door + dn ~ s_r, value.var = "sf6_conc") %>%
  .[, r_upon_s := r/s * 100] %>%
  .[!is.na(dn)] %>%
  .[, repeats := rleid(date(datetime)), by = .(building_type, receptor_door, dn)] %>%
  .[building_type %like% "Flash", building_type := "Flash façade"] %>%
  ggplot( aes(paste0("Door ", receptor_door, "\n", dn), r_upon_s, color = paste(repeats)) ) +
  geom_boxplot( ) +
  stat_summary(fun.y = "mean", geom = "point", shape = 23, size = 2, fill = "white", position = position_dodge(0.75)) +
  ylab("The SF6 concentration ratio between receptor and source rooms (%)") +
  xlab("Scenarios") +
  scale_color_brewer("Exp repeat ID", palette = "Accent") +
  theme(legend.position = "top") #+
  # theme_classic()

p + facet_wrap(vars(building_type))+ coord_cartesian(ylim = c(0,1))

```

### Fixed scale (at 35%, the global max)
```{r echo=FALSE, fig.height=5, fig.width=8, warning=FALSE}
p + facet_wrap(vars(building_type))+ coord_cartesian(ylim = c(0,35))
```

### Flexible scale
```{r echo=FALSE, fig.height=5, fig.width=8, warning=FALSE}
p + facet_wrap(vars(building_type), scales = "free") 
```


## `Downstair` upon `source room` ratio 

### Fixed scale (at 1%)

```{r echo=FALSE, fig.height=5, fig.width=8, warning=FALSE}
dt_innova[hour(datetime) %in% c(12:14), dn := "Daytime"]
dt_innova[hour(datetime) %in% c(18:20), dn := "Nighttime"]

dt_innova %>% setorder(datetime)
dt_innova[, time_index := seq.int(1:.N), by = .(exp_id, innova_ch)]

p <-
  dt_innova[test_type == "Test" & time_index > 4 ] %>% 
  dcast(datetime + building_type + receptor_door + dn ~ paste(s_r,loc), value.var = "sf6_conc") %>% clean_names %>% 
  .[, r_upon_s := downstair/s_room * 100] %>%
  .[!is.na(dn)] %>%
  .[, repeats := rleid(date(datetime)), by = .(building_type, receptor_door, dn)] %>%
  .[building_type %like% "Flash", building_type := "Flash façade"] %>%
   ggplot( aes(paste0("Door ", receptor_door, "\n", dn), r_upon_s, color = paste(repeats)) ) +
  geom_boxplot( ) +
  stat_summary(fun.y = "mean", geom = "point", shape = 23, size = 2, fill = "white", position = position_dodge(0.75)) +
  ylab("The SF6 concentration ratio between downstair and source room (%)") +
  xlab("Scenarios") +
  scale_color_brewer("Exp repeat ID", palette = "Accent") +
  theme(legend.position = "top") #+
  # theme_classic()

p + facet_wrap(vars(building_type))+ coord_cartesian(ylim = c(0,1))
```

### Fixed scale (at 35%, the global max)
```{r echo=FALSE, fig.height=5, fig.width=8, warning=FALSE}
p + facet_wrap(vars(building_type))+ coord_cartesian(ylim = c(0,35))
```

### Flexible scale
```{r echo=FALSE, fig.height=5, fig.width=8, warning=FALSE}
p + facet_wrap(vars(building_type), scales = "free") 
```

## `Receptor window` upon `source room` ratio 
### Fixed scale (at 1%)
```{r echo=FALSE, fig.height=5, fig.width=8, warning=FALSE}
dt_innova[hour(datetime) %in% c(12:14), dn := "Daytime"]
dt_innova[hour(datetime) %in% c(18:20), dn := "Nighttime"]

dt_innova %>% setorder(datetime)
dt_innova[, time_index := seq.int(1:.N), by = .(exp_id, innova_ch)]

p <-
  dt_innova[test_type == "Test" & time_index > 4 ] %>% 
  dcast(datetime + building_type + receptor_door + dn ~ paste(s_r,loc), value.var = "sf6_conc") %>% clean_names %>% 
  .[, r_upon_s := r_window/s_room * 100] %>%
  .[!is.na(dn)] %>%
  .[, repeats := rleid(date(datetime)), by = .(building_type, receptor_door, dn)] %>%
  .[building_type %like% "Flash", building_type := "Flash façade"] %>%
   ggplot( aes(paste0("Door ", receptor_door, "\n", dn), r_upon_s, color = paste(repeats)) ) +
  geom_boxplot( ) +
  stat_summary(fun.y = "mean", geom = "point", shape = 23, size = 2, fill = "white", position = position_dodge(0.75)) +
  ylab("The SF6 concentration ratio between receptor window and source room (%)") +
  xlab("Scenarios") +
  scale_color_brewer("Exp repeat ID", palette = "Accent") +
  theme(legend.position = "top") #+
  # theme_classic()

p + facet_wrap(vars(building_type))+ coord_cartesian(ylim = c(0,1))
```

### Fixed scale (at 35%, the global max)
```{r echo=FALSE, fig.height=5, fig.width=8, warning=FALSE}
p + facet_wrap(vars(building_type))+ coord_cartesian(ylim = c(0,35))
```

### Flexible scale
```{r echo=FALSE, fig.height=5, fig.width=8, warning=FALSE}
p + facet_wrap(vars(building_type), scales = "free") 
```


## Summary table
```{r warning=FALSE}
dt_1 <- dt_innova[test_type == "Test" & time_index > 4 ] %>% 
  dcast(datetime + building_type + receptor_door + dn ~ paste(s_r,loc), value.var = "sf6_conc") %>% clean_names %>%
      .[, r_room_upon_s_room := r_room/s_room * 100] %>%
      .[, r_window_upon_s_room := r_window/s_room * 100] %>%
      .[, downstair_upon_s_room := downstair/s_room * 100] %>%
  .[!is.na(dn)] %>%
  .[, repeats := rleid(date(datetime)), by = .(building_type, receptor_door, dn)] %>%
  .[building_type %like% "Flash", building_type := "Flash façade"] %>% 
  .[, .(r_room_upon_s_room_mean = mean(r_room_upon_s_room, na.rm = T),
        r_room_upon_s_room_median = median(r_room_upon_s_room, na.rm = T),
        r_window_upon_s_room_mean = mean(r_window_upon_s_room, na.rm = T),
        r_window_upon_s_room_median = median(r_window_upon_s_room, na.rm = T),
        downstair_upon_s_room_mean = mean(downstair_upon_s_room, na.rm = T),
        downstair_upon_s_room_median = median(downstair_upon_s_room, na.rm = T)) , by = .(building_type, receptor_door,dn,date = date(datetime),repeats)]

dt_1 %>% datatable(rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) %>%
    formatRound(columns=c('r_room_upon_s_room_mean',
'r_room_upon_s_room_median',
'r_window_upon_s_room_mean',
'r_window_upon_s_room_median',
'downstair_upon_s_room_mean' ,
'downstair_upon_s_room_median'), digits=2)
# DT::datatable(dt_)

```



```{r warning=FALSE, fig.height= 10, fig.width= 8}
dt_2 <- dt_innova[test_type == "Test" & time_index > 4 ] %>% 
  dcast(datetime + building_type + receptor_door + dn ~ paste(s_r,loc), value.var = "sf6_conc") %>% clean_names %>%
      .[, r_room_upon_s_room := r_room/s_room * 100] %>%
      .[, r_window_upon_s_room := r_window/s_room * 100] %>%
      .[, downstair_upon_s_room := downstair/s_room * 100] %>%
  .[!is.na(dn)] %>%
  .[, repeats := rleid(date(datetime)), by = .(building_type, receptor_door, dn)] %>%
  .[building_type %like% "Flash", building_type := "Flash façade"] %>% 
  .[, .(`Receptor room upon source room` = mean(r_room_upon_s_room, na.rm = T),
        # r_room_upon_s_room_median = median(r_room_upon_s_room, na.rm = T),
       `Receptor window upon source room` = mean(r_window_upon_s_room, na.rm = T),
        # r_window_upon_s_room_median = median(r_window_upon_s_room, na.rm = T),
        `Downstair upon source room` = mean(downstair_upon_s_room, na.rm = T)#,
        # downstair_upon_s_room_median = median(downstair_upon_s_room, na.rm = T)
        ) , by = .(building_type, receptor_door,dn,date = date(datetime),repeats)] 
  
dt_2 %>% melt(id.vars = c("building_type", "receptor_door", "dn", "date", "repeats") ) %>%
  ggplot( aes(paste0("Door ", receptor_door, "\n", dn), value, fill = paste(repeats)) ) +
  geom_col(position = "dodge") +
  ylab("The SF6 concentration ratio between different locations and source room (%)") +
  xlab("Scenarios") +
  scale_fill_brewer("Exp repeat ID", palette = "Accent") +
  # facet_wrap(vars(building_type, variable), scales = "free") +
  
  facet_grid(variable~building_type) +
  theme(legend.position = "top") 
  
```

<!-- ```{r} -->

<!-- fun_mean <- function(x) 8 -->
<!-- fun_median <- function(x) 7 -->
<!-- fun_mean <- function(x) 6 -->

<!-- dt_innova[test_type == "Test" & loc == "room" & time_index > 4 ] %>%  -->
<!--   dcast(datetime + building_type + receptor_door + dn ~ s_r, value.var = "sf6_conc") %>%  -->
<!--   .[, r_upon_s := r/s * 100] %>% -->
<!--   .[!is.na(dn)] %>% -->
<!--   .[, repeats := rleid(date(datetime)), by = .(building_type, receptor_door, dn)] %>% -->
<!--   .[building_type %like% "Flash", building_type := "Flash façade"] %>% -->
<!--   .[, R_] -->


<!--   ggplot( aes(paste0("Receptor door: ", receptor_door, "\n", dn), r_upon_s, color = paste(repeats)) ) +  -->
<!--   geom_boxplot( ) + -->
<!--   # stat_summary(fun.y = "mean", geom = "text",  -->
<!--   #              aes(label=signif(..y..,4)), position = position_dodge(0.75)) + -->
<!--     stat_summary(fun.y = "fun_mean", fun.ymin = "mean", geom = "text",  -->
<!--                aes(label=signif(..ymin..,2)), position = position_dodge(0.75)) + -->
<!--       stat_summary(fun.y = "fun_median", fun.ymin = "median", geom = "text",  -->
<!--                aes(label=signif(..ymin..,2)), position = position_dodge(0.75)) + -->
<!--   ylab("The SF6 concentration ratio between receptor and source rooms (%)") + -->
<!--   xlab("Scenarios") + -->
<!--   scale_color_manual("Exp repeat ID", values = nea_colors) + -->
<!--   theme(legend.position = "top") + -->
<!--   theme_classic() -->

<!-- ``` -->


## Time-resolved transmission rate

```{r echo=FALSE}
df_4 <- dt_innova[, date := date(datetime)]

ui_1 <- fluidPage(
  fluidRow(
    column(3,
      dateInput(
      'date',
      'Select Date',
      value = max(df$date),
      min = min(df$date),
      max = max(df$date),
      datesdisabled = setdiff(seq.Date(min(df_4$date), max(df_4$date), by = "day"), df_4$date %>% unique) %>% as_date
    )
    ),
    column(9,
    sliderInput(
      "timeRange",
      label = "Select Time Range",
      min = as.POSIXct("9:00:00", format = "%H:%M:%S", tz = "Singapore"),
      max = as.POSIXct("22:00:00", format = "%H:%M:%S", tz = "Singapore"),
      value = c(
        as.POSIXct("10:00:00", format = "%H:%M:%S", tz = "Singapore"),
        as.POSIXct("21:00:00", format = "%H:%M:%S", tz = "Singapore")
      ),
      timeFormat = "%H:%M:%S"
    )
  )),
  fluidRow(
    column(12,
    mainPanel(
      plotlyOutput("timeseriesPlot")
    )
    )
  )
)

# Define server logic for timeseries plot
server_1 <- function(input, output) {
  output$timeseriesPlot <- renderPlotly({

    
filteredData <- copy(df_4)[date == input$date] %>% 
  .[hour(datetime) * 60 + minute(datetime) >= hour(input$timeRange[1]) * 60 + minute(input$timeRange[1]) + 8*60] %>%
  .[hour(datetime) * 60 + minute(datetime) <= hour(input$timeRange[2]) * 60 + minute(input$timeRange[2]) + 8*60] %>%
  dcast(datetime + building_type + receptor_door ~ paste(s_r,loc), value.var = "sf6_conc") %>% clean_names %>% 
  .[, r_room_upon_s_room := r_room/s_room * 100] %>%
  .[, r_windor_upon_s_room := r_window/s_room * 100] %>%
  .[, downstair_upon_s_room := downstair/s_room * 100] %>%
  .[, repeats := rleid(date(datetime)), by = .(building_type, receptor_door)] %>% 
  melt(id.vars = c("datetime", "building_type", "receptor_door", "repeats"), 
       measure.vars = c("r_room_upon_s_room", "r_windor_upon_s_room", "downstair_upon_s_room"))


    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ value,
      color = ~ variable,
      type = 'scatter',
      mode = 'lines' #,
      # colors = s_r_loc_colors
    ) %>%
      layout(
        title = NULL#,"\n", 
          # "Receptor door: ", filteredData$receptor_door %>% unique ,"\n", 
          # "Building type: ", filteredData$building_type %>% unique
          ,
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = "The SF6 concentration ratio between different locations and source room (%)"
         ),
        legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.5,
                     y = 1.1),
        # autosize = F, 
        width = 700, height = 500
      )
  })
}

# Run the app
shinyApp(ui = ui_1, server = server_1, options = list(height = 650) )
```


## Temperature differences

$$ \Delta T = Temperature_{window} - Temperature_{room} $$ 
```{r}
df_5 <- dt_velocicalc[, date := date(datetime)]

ui_1 <- fluidPage(
  fluidRow(
    column(3,
      dateInput(
      'date',
      'Select Date',
      value = max(df_5$date),
      min = min(df_5$date),
      max = max(df_5$date),
      datesdisabled = setdiff(seq.Date(min(df_5$date), max(df_5$date), by = "day"), df_5$date %>% unique) %>% as_date
    )
    ),
),
  fluidRow(
    column(12,
    mainPanel(
      plotlyOutput("timeseriesPlot")
    )
    )
  )
)

# Define server logic for timeseries plot
server_1 <- function(input, output) {
  output$timeseriesPlot <- renderPlotly({

    # df_5[date == ymd("2023-08-14")]%>%
    #   dcast(datetime + date + s_r + test_type + receptor_door ~  loc, value.var = "temperature") %>%
    #   .[, delta_t := window - room] %>%
    #   .[s_r == "s", s_r := "Source"] %>%
    #   .[s_r == "r", s_r := "Receptor"]
    # 
    
    filteredData <- copy(df_5)[date == input$date] %>%
      dcast(datetime + date + s_r + test_type + receptor_door ~  loc, value.var = "temp") %>%
      .[, delta_t := window - room] %>%
      .[s_r == "s", s_r := "Source"] %>%
      .[s_r == "r", s_r := "Receptor"]
    
    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ delta_t,
      color = ~ s_r,
      type = 'scatter',
      mode = 'lines' #,
      # colors = s_r_loc_colors
    ) %>%
      layout(
        title = NULL#,"\n", 
          # "Receptor door: ", filteredData$receptor_door %>% unique ,"\n", 
          # "Building type: ", filteredData$building_type %>% unique
          ,
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable
        ),
        legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.5,
                     y = 1.1),
        # autosize = F, 
        width = 750, height = 500
      )
  })
}

# Run the app
shinyApp(ui = ui_1, server = server_1, options = list(height = 650) )
```
