---
title: "Analysis"
author: "Jiayu Li"
date: "17 July 2023"
output:
  html_document:
    toc: true
    theme: united
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read data, include=FALSE}
source("R/read_clean_data_without_condi.R")
library(plotly)
library(DT)
library(shiny)
```

```{r read condition files, echo=FALSE}
cond_general_scenario <- fread("clean_data/conditions/general_scenario.csv")
cond_innova_vc <- fread("clean_data/conditions/innova_vc.csv")
cond_source_and_receptor <- fread("clean_data/conditions/source_and_receptor.csv")
cond_wind_sensor <- fread("clean_data/conditions/wind_sensor.csv")

# cond_general_scenario[, start_datetime := dmy_hm(paste(exp_date, start_time) ) - hours(8)]
# cond_general_scenario[, end_datetime := dmy_hm(paste(exp_date, end_time) )- hours(8)]

cond_general_scenario[, start_datetime := dmy_hm(paste(exp_date, start_time) ) ]
cond_general_scenario[, end_datetime := dmy_hm(paste(exp_date, end_time) ) ]
```

# Conditions

<!-- ```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE} -->

<!-- cond_general_scenario[, note := iconv(note, to = "utf-8")] -->

<!-- copy(cond_general_scenario)  %>%  -->

<!--   .[, start_datetime := start_datetime - hours(8)] %>%  # this is only correcting the error in the table display -->

<!--    .[, end_datetime := end_datetime - hours(8)] %>%  # this is only correcting the error in the table display -->

<!--   datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) %>% formatDate(c("start_datetime","end_datetime"), method = "toLocaleString") -->

<!-- ``` -->

<!-- ## Innova conditions -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->

<!--     cond_innova_vc %>% -->

<!--   datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) -->

<!-- ``` -->

<!-- ## Source and receptor conditions -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->

<!--     cond_source_and_receptor%>% -->

<!--   datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) -->

<!-- ``` -->

<!-- ## Wind sensor conditions -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->

<!--     cond_wind_sensor %>% -->

<!--   datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) -->

<!-- ``` -->

## Add general conditions

```{r add conditions general, echo=TRUE}
add_general_condition <- function(dt, dt_condi) {
  for (i in 1:length(dt_condi$start_datetime) ) {
    dt[datetime >= dt_condi$start_datetime[i] & datetime <= dt_condi$end_datetime[i],
       `:=`(test_id = dt_condi$test_id[i],
            exp_id = dt_condi$exp_id[i],
            sf6_rate = dt_condi$sf6_rate[i],
            building_type = dt_condi$building_type[i],
            scenario = dt_condi$scenario[i],
            test_type = dt_condi$test_type[i],
            receptor_door = dt_condi$receptor_door[i]
            )]
  }
}

add_general_condition(dt_velocicalc, cond_general_scenario)
add_general_condition(dt_innova, cond_general_scenario)
add_general_condition(dt_wind_sensor, cond_general_scenario)
```

## Add VelociCalc conditions

```{r add conditions velocicalc, echo=TRUE}
dt_velocicalc <- cond_source_and_receptor[cond_innova_vc,
                                          on = .(test_id, s_r)][vc_unit != ""][dt_velocicalc, on =
                                                                                 .(test_id, s_r, loc, vc_unit)] %>%
  .[!is.na(test_id)]
```

## Add Innova conditions

```{r add conditions innova, echo=TRUE}
dt_innova <- cond_source_and_receptor[cond_innova_vc,
                                      on = .(test_id, s_r)][dt_innova,
                                                            on = .(test_id, innova_ch)] %>%
  .[!is.na(test_id)]
```

## Add Wind sensor conditions and calculate `u`, `v`, and `w` (need double-check)

(Please check if my understanding is correct or not.)

`u` and `v` use the data from the sensors marked "h", and `w` uses the data from the sensors marked "v". The equations for calculation `u`, `v`, and `w` are as follows. $$
u = WIMWV_{<3>} * \sin(\frac{WIMWV_{<1>} * \pi}{180})
$$ $$
v = WIMWV_{<3>} * \cos(\frac{WIMWV_{<1>} * \pi}{180})
$$ $$
w = -WIMWV_{<3>} * \cos(\frac{WIMWV_{<1>} * \pi}{180})
$$

```{r add conditions, echo=TRUE}
dt_wind_sensor_ws_wd <- cond_source_and_receptor[cond_wind_sensor,
                                           on = .(test_id, s_r, room_type)][dt_wind_sensor,
                                                                            on = .(test_id, wind_sensor_unit)] %>%
  .[!is.na(test_id)]

dt_wind_sensor_ws_wd[position == "h", u := vel_mag_WIMWV_3 * sin(vel_angle_WIMWV_1 * pi/180)]
dt_wind_sensor_ws_wd[position == "h", v := vel_mag_WIMWV_3 * cos(vel_angle_WIMWV_1 * pi/180)]
dt_wind_sensor_ws_wd[position == "v", w := - vel_mag_WIMWV_3 * cos(vel_angle_WIMWV_1 * pi/180)]

# correct test_id == 9 that "the MARKER was facing to outside of the room."
dt_wind_sensor_ws_wd[test_id == 9, u := -u]
dt_wind_sensor_ws_wd[test_id == 9, v := -v]

cols <- names(dt_wind_sensor_ws_wd)[c(1:9, 12:14,21:26)]

dt_wind_sensor <- dt_wind_sensor_ws_wd[, lapply (.SD, mean, na.rm = T), .SDcols = c(
    "u",
    "v",
    "w"
  ), by = cols]

```

<!-- # Raw data -->

<!-- Please note that the `experimental ID` is relabeled according to the condition table (the `exp_id` column) in [this link](https://jiayuliaq.shinyapps.io/check_raw_data_shiny/). Among `r max(cond_general_scenario$exp_id)` `experimental IP`, some are real experimental "test", some are "ACH" decay test, and others are "trail" or "invalid" as labeled as `Test type` in the plot title. -->

# Innova

## Raw data

```{r echo=FALSE}
df <- dt_innova[, date := date(datetime)]

ui_1 <- fluidPage(sidebarLayout(
  sidebarPanel(
    # selectInput('exp_id', 'Select experiment ID', choices = sort(unique(df$exp_id)), selected = 13),
    dateInput(
      'date',
      'Select Date',
      value = max(df$date),
      min = min(df$date),
      max = max(df$date),
      datesdisabled = setdiff(seq.Date(min(df$date), max(df$date), by = "day"), df$date %>% unique) %>% as_date
    ),
    selectInput('variable', 'Select Parameter', c('sf6_conc')),
    checkboxInput('log', 'Logarithmic Scale', FALSE)  # Checkbox for logarithmic scale
  ),
  
  mainPanel(plotlyOutput("timeseriesPlot"))
))

# Define server logic for timeseries plot
server_1 <- function(input, output) {
  output$timeseriesPlot <- renderPlotly({

    # filteredData <- copy(df)[exp_id == input$exp_id]
    filteredData <- copy(df)[date == input$date]
    
    filteredData[s_r == "s", s_r := "Source"]
    filteredData[s_r == "r", s_r := "Receptor"]
    
    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ get(input$variable),
      color = ~ paste(s_r, loc),
      type = 'scatter',
      mode = 'lines'
    ) %>%
      layout(
        title = NULL,
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable,
          type = ifelse(input$log, "log", "linear")
        )
      )
  })
}

# Run the app
shinyApp(ui = ui_1, server = server_1)
```

# VelociCalc

## Raw data

```{r echo=FALSE}
df_2 <- dt_velocicalc

ui_1 <- fluidPage(

  sidebarLayout(
    sidebarPanel(
      selectInput('exp_id', 'Select experiment ID', choices = sort(unique(df_2$exp_id)), selected = 13),
      selectInput('variable', 'Select Parameter', c('vel','temperature',"RH"))
    ),

    mainPanel(
      plotlyOutput("timeseriesPlot")
    )
  )
)

# Define server logic for timeseries plot
server_1 <- function(input, output) {
  output$timeseriesPlot <- renderPlotly({

    filteredData <- copy(df_2)[exp_id == input$exp_id]
    
    filteredData[s_r == "s", s_r := "Source"]
    filteredData[s_r == "r", s_r := "Receptor"]
    
    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ get(input$variable),
      color = ~ paste(s_r, loc),
      type = 'scatter',
      mode = 'lines'
    ) %>%
      layout(
        title = paste0("Test type: ", filteredData$test_type%>% unique#,"\n", 
          # "Receptor door: ", filteredData$receptor_door %>% unique ,"\n", 
          # "Building type: ", filteredData$building_type %>% unique
          ),
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable
        )
      )
  })
}

# Run the app
shinyApp(ui = ui_1, server = server_1)
```

# Wind sensor

## Raw data

```{r echo=FALSE}
df_3 <- dt_wind_sensor

ui_1 <- fluidPage(

  sidebarLayout(
    sidebarPanel(
      selectInput('exp_id', 'Select experiment ID', choices = sort(unique(df_3$exp_id)), selected = 13),
      selectInput('variable', 'Select Parameter', c('u','v',"w"))
    ),

    mainPanel(
      plotlyOutput("timeseriesPlot")
    )
  )
)

# Define server logic for timeseries plot
server_1 <- function(input, output) {
  output$timeseriesPlot <- renderPlotly({

    filteredData <- copy(df_3)[exp_id == input$exp_id]
    
    filteredData[s_r == "s", s_r := "Source"]
    filteredData[s_r == "r", s_r := "Receptor"]
    
    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ get(input$variable),
      color = ~ paste(s_r, loc, room_type),
      type = 'scatter',
      mode = 'lines'
    ) %>%
      layout(
        title = paste0("Test type: ", filteredData$test_type%>% unique#,"\n", 
          # "Receptor door: ", filteredData$receptor_door %>% unique ,"\n", 
          # "Building type: ", filteredData$building_type %>% unique
          ),
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable
        )
      )
  })
}

# Run the app
shinyApp(ui = ui_1, server = server_1)
```

```{r eval=FALSE, include=FALSE}

dt_innova[hour(datetime) %in% c(9:14), dn := "Daytime"]
dt_innova[hour(datetime) %in% c(18:20), dn := "Nighttime"]
dt_innova %>% setorder(datetime)
dt_innova[, time_index := seq.int(1:.N), by = .(exp_id, innova_ch)]

library(ggplot2)
dt_innova[time_index > 5 & test_type == "Test" & !is.na(dn)] %>% ggplot() +
  geom_boxplot(aes(paste(exp_id),  sf6_conc, color = dn)) +
  scale_y_log10()

```

## Wind rose

All the calculationa and plots are based on the data from the `$WIMWV` section.

```{r wind rose, echo=FALSE}
library(openair)
df <- dt_innova[, date := date(datetime)]

# df[, datetime := datetime - hours(8)]
ui_4 <- fluidPage(
  sidebarLayout(
  sidebarPanel(
    # selectInput('exp_id', 'Select experiment ID', choices = sort(unique(df$exp_id)), selected = 13),
    dateInput(
      'date',
      'Select Date',
      value = max(df$date),
      min = min(df$date),
      max = max(df$date),
      datesdisabled = setdiff(seq.Date(min(df$date), max(df$date), by = "day"), df$date %>% unique) %>% as_date
    ),
    sliderInput(
      "timeRange",
      label = "Select Time Range",
      min = as.POSIXct("9:00:00", format = "%H:%M:%S", tz = "Singapore"),
      max = as.POSIXct("22:00:00", format = "%H:%M:%S", tz = "Singapore"),
      value = c(
        as.POSIXct("13:00:00", format = "%H:%M:%S", tz = "Singapore"),
        as.POSIXct("14:00:00", format = "%H:%M:%S", tz = "Singapore")
      ),
      timeFormat = "%H:%M:%S"
    )  # Time range slider
    # sliderInput(
    #   "timeRange",
    #   label = "Select Time Range",
    #   min = min(df$datetime),
    #   max = max(df$datetime),
    #   value = c(
    #     min(df$datetime),
    #     max(df$datetime)
    #   ),
    #   timeFormat = "%H:%M:%S"
    # )  # Time range slider
    
    # selectInput('variable', 'Select Parameter', c('sf6_conc'))
  ),
  
  mainPanel(plotOutput("timeseriesPlot"))
))

# Define server logic for timeseries plot
server_4 <- function(input, output) {
    
  
  output$timeseriesPlot <- renderPlot({
# to solve the issue that wind direction cannot be averaged (seems no different)
# dt_wind_sensor_ws_wd[, datetime := floor_date(datetime, unit = "5 minutes")]
# 
# dt_wind_sensor_ws_wd[, WIMDA_u := vel_mag_WIMDA_19 * sin(vel_angle_WIMDA_13 * pi/180)]
# dt_wind_sensor_ws_wd[, WIMDA_v := vel_mag_WIMDA_19 * cos(vel_angle_WIMDA_13 * pi/180)]
# 
# dt_wind_sensor_ws_wd[, WIMWV_u := vel_mag_WIMWV_3 * sin(vel_angle_WIMWV_1 * pi/180)]
# dt_wind_sensor_ws_wd[, WIMWV_v := vel_mag_WIMWV_3 * cos(vel_angle_WIMWV_1 * pi/180)]
# 
# 
# dt_wind_sensor_ws_wd <-
#   dt_wind_sensor_ws_wd[, lapply (.SD, mean, na.rm = T), .SDcols = c(
#     "WIMDA_u",
#     "WIMDA_v",
#     "WIMWV_u",
#     "WIMWV_v",
#     "vel_mag_WIMDA_19",
#     "vel_mag_WIMWV_3",
#     "temp_WIMDA_5",
#     "rh_WIMDA_9"
#   ), by = .(datetime, wind_sensor_unit)]
# 
# dt_wind_sensor_ws_wd[, vel_angle_WIMDA_13 := (atan2(WIMDA_u, WIMDA_v) * 360/2/pi) + 180]
# dt_wind_sensor_ws_wd[, vel_angle_WIMWV_1 := (atan2(WIMWV_u, WIMWV_v) * 360/2/pi) + 180]

# start_time <- 11
# end_time <- 14

    # df %>%
    #   filter(as_date(datetime) == ymd(input$date), sensor == input$sensor,
    #          hour(datetime) * 60 + minute(datetime) >= hour(input$timeRange[1]) * 60 + minute(input$timeRange[1]), 
    #          hour(datetime) * 60 + minute(datetime) <= hour(input$timeRange[2]) * 60 + minute(input$timeRange[2])) %>%
    #   select(datetime, input$variable, sensor)
  
filteredData_1 <- copy(dt_wind_sensor_ws_wd)[position == "h" &
                                       date(datetime) == ymd(input$date) ]
filteredData  <-  
  filteredData_1[hour(datetime) * 60 + minute(datetime) >= hour(input$timeRange[1]) * 60 + minute(input$timeRange[1]) + 8*60] %>%
  .[hour(datetime) * 60 + minute(datetime) <= hour(input$timeRange[2]) * 60 + minute(input$timeRange[2]) + 8*60]

filteredData[, type_ := room_type]
filteredData[s_r == "s", type_ := paste(room_type, "Source")]
filteredData[s_r == "r", type_ := paste(room_type, "Receptor")]


windRose(
  mydata = filteredData,
  ws = "vel_mag_WIMWV_3",
  wd = "vel_angle_WIMWV_1",
  type = "type_",
  main = paste("For the selected date, please only select time between:",  format(min(filteredData_1$datetime), format = "%H:%M:%S"), "and", format(max(filteredData_1$datetime), format = "%H:%M:%S"))
)

# filteredData %>% ggplot() + geom_line(aes(datetime, vel_mag_WIMWV_3, color = type_))
  })
}

# Run the app
shinyApp(ui = ui_4, server = server_4)

```
