---
title: "Check raw data and experimental conditions"
author: "Jiayu Li"
date: "14 July 2023"
output:
  html_document:
    toc: true
    theme: united
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read data, include=FALSE}
# source("R/funcitons.R")
library(magrittr)
library(data.table)
library(lubridate)
library(plotly)
library(DT)
library(shiny)
library(ggplot2)
library(janitor)
library(tidyr)
library(dplyr)

dt_innova <- fread("clean_data_1_min/innova/dt_innova.csv")
dt_velocicalc <- fread("clean_data_1_min/velocicalc/dt_velocicalc.csv")
dt_wind_sensor <- fread("clean_data_1_min/wind_sensor/dt_wind_sensor.csv")

dt_innova <- dt_innova[!( datetime >= ymd_hm("2023-05-04 12:40") & datetime <= ymd_hm("2023-05-04 14:05") & innova_ch == 5)]

# dt_innova[datetime >= ymd_hm("2023-05-04 12:40") & datetime <= ymd_hm("2023-05-04 14:05")]
```


```{r echo=FALSE}
cond_general_scenario <- fread("clean_data/conditions/general_scenario.csv")
cond_innova_vc <- fread("clean_data/conditions/innova_vc.csv")
cond_source_and_receptor <- fread("clean_data/conditions/source_and_receptor.csv")
cond_wind_sensor <- fread("clean_data/conditions/wind_sensor.csv")

# cond_general_scenario[, start_datetime := dmy_hm(paste(exp_date, start_time) ) - hours(8)]
# cond_general_scenario[, end_datetime := dmy_hm(paste(exp_date, end_time) )- hours(8)]
```

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- dt_velocicalc %>% setorder(datetime) -->
<!-- dt_innova %>% setorder(datetime) -->
<!-- dt_wind_sensor %>% setorder(datetime) -->
<!-- ``` -->

# Raw data
## Innova
```{r echo=FALSE}
df <- dt_innova[, date := date(datetime)]

ui_1 <- fluidPage(
  # titlePanel("Time Series Data Viewer"),

  sidebarLayout(
    sidebarPanel(
      dateInput('date', 'Select Date', value = max(df$date), min = min(df$date), max = max(df$date),
                datesdisabled = setdiff(seq.Date(min(df$date), max(df$date), by = "day"), df$date %>% unique) %>% as_date),
      # selectInput('date', 'Select Date', choices = unique(as_date(df$datetime))),
      
      selectInput('variable', 'Select Parameter', c('sf6_conc')),
      checkboxInput('log', 'Logarithmic Scale', FALSE)  # Checkbox for logarithmic scale
   
    ),

    mainPanel(
      plotlyOutput("timeseriesPlot")
    )
  )
)

# Define server logic for timeseries plot
server_1 <- function(input, output) {
  output$timeseriesPlot <- renderPlotly({

    filteredData <- df %>%
      filter(date == ymd(input$date)) %>%
      select(datetime, input$variable, innova_ch)

    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ get(input$variable),
      color = ~ paste("Ch.", innova_ch),
      type = 'scatter',
      mode = 'lines'
    ) %>%
      layout(
        title = paste(input$variable, 'on', input$date),
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable,
          type = ifelse(input$log, "log", "linear")
        )
      )
  })
}

# Run the app
shinyApp(ui = ui_1, server = server_1)
```

## VelociCalc
```{r echo=FALSE}
df_2 <- dt_velocicalc[, date := date(datetime)]

ui_2 <- fluidPage(
  # titlePanel("Time Series Data Viewer"),

  sidebarLayout(
    sidebarPanel(
      dateInput('date', 'Select Date', value = max(df_2$date), min = min(df_2$date), max = max(df_2$date),
                datesdisabled = setdiff(seq.Date(min(df_2$date), max(df_2$date), by = "day"), df_2$date %>% unique) %>% as_date),
      
      selectInput('variable', 'Select Parameter', c('vel', 'temperature','RH')) #,
      # checkboxInput('log', 'Logarithmic Scale', FALSE)  # Checkbox for logarithmic scale
   
    ),

    mainPanel(
      plotlyOutput("timeseriesPlot")
    )
  )
)

# Define server logic for timeseries plot
server_2 <- function(input, output) {
  output$timeseriesPlot <- renderPlotly({

    filteredData <- df_2 %>%
      filter(date == ymd(input$date)) %>%
      select(datetime, input$variable, equip_unit)

    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ get(input$variable),
      color = ~ equip_unit,
      type = 'scatter',
      mode = 'lines'
    ) %>%
      layout(
        title = paste(input$variable, 'on', input$date),
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable#,
          # type = ifelse(input$log, "log", "linear")
        )
      )

  })
}

# Run the app
shinyApp(ui = ui_2, server = server_2)
```

## Wind Sensor

### Calculate `u`, `v`, and `w` (need double-check)

(Please check if my understanding is correct or not.)

`u` and `v` use the data from the sensors marked "h", and `w` uses the data from the sensors marked "v". The equations for calculation `u`, `v`, and `w` are as follows. 

$$
u = WIMWV_{<3>} * \sin(\frac{WIMWV_{<1>} * \pi}{180})
$$ 
$$
v = WIMWV_{<3>} * \cos(\frac{WIMWV_{<1>} * \pi}{180})
$$ 
$$
w = -WIMWV_{<3>} * \cos(\frac{WIMWV_{<1>} * \pi}{180})
$$


```{r echo=FALSE}
wind_sensor_loc <- cond_wind_sensor[,c("wind_sensor_unit","position")] %>% unique 

df_3 <- wind_sensor_loc[dt_wind_sensor, 
                on = .(wind_sensor_unit)][wind_sensor_unit %in% c(12,10), 
                                          sensor_tree := "1: 12(h); 10(v)"][wind_sensor_unit %in% c(5,7), 
                                          sensor_tree := "2: 5(h); 7(v)"][wind_sensor_unit %in% c(11,1), 
                                          sensor_tree := "3: 11(h); 1(v)"][, date := date(datetime)]

# df_3[position == "h", u := vel_mag_WIMWV_3 * sin(vel_angle_WIMWV_1 * pi/180)]
df_3[position == "h", u_from_horizontal_sensor := vel_mag_WIMWV_3 * sin(vel_angle_WIMWV_1 * pi/180)]
df_3[position == "v", u_from_vertical_sensor := vel_mag_WIMWV_3 * sin(vel_angle_WIMWV_1 * pi/180)]
df_3[position == "h", v := vel_mag_WIMWV_3 * cos(vel_angle_WIMWV_1 * pi/180)]
df_3[position == "v", w := - vel_mag_WIMWV_3 * cos(vel_angle_WIMWV_1 * pi/180)]


ui <- fluidPage(

  fluidRow(column(4,
      dateInput('date', 'Select Date', value = max(df_3$date), min = min(df_3$date), max = max(df_3$date),
                datesdisabled = setdiff(seq.Date(min(df_3$date), max(df_3$date), by = "day"), df_3$date %>% unique) %>% as_date),
      titlePanel("Very raw data"),
      selectInput('variable', 'Select Parameter', c('vel_mag_WIMWV_3', 
                                                    'vel_mag_WIMDA_19', 
                                                    'vel_angle_WIMWV_1',
                                                    'vel_angle_WIMDA_13',
                                                    'temp_WIMDA_5',
                                                    'rh_WIMDA_9'))
      # checkboxInput('log', 'Logarithmic Scale', FALSE)  # Checkbox for logarithmic scale
   
    )),

    fluidRow(column(12,
                          plotlyOutput("timeseriesPlot_1")
    )),
  fluidRow(column(12, titlePanel("The three velocity components"))),
  fluidRow(column(4,
                  selectInput(
                    'variable_2', 'Select Parameter', c(#'u',
                                                        'u_from_horizontal_sensor',
                                                        'u_from_vertical_sensor',
                                                        'v',
                                                        'w')
                  ))), 
      fluidRow(column(12,
                          plotlyOutput("timeseriesPlot_2")
    ))
    )


# Define server logic for timeseries plot
server <- function(input, output) {
  output$timeseriesPlot_2 <- renderPlotly({

    filteredData <- copy(df_3) %>% .[, lapply (.SD, mean, na.rm = T), .SDcols = c(#'u',
                                                        'u_from_horizontal_sensor',
                                                        'u_from_vertical_sensor',
                                                        'v',
                                                        'w'), by = .(datetime,sensor_tree,date)] %>%
      filter(date == ymd(input$date)) %>%
      select(datetime, input$variable_2, sensor_tree) %>%
  setorder(sensor_tree, datetime) %>%
  drop_na(c(input$variable_2)) 
      
      
  plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ get(input$variable_2),
      color = ~ paste("Tree",sensor_tree),
      # type = 'scatter',
      mode = 'lines+markers'
    ) %>%
      layout(
        title = NULL,
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable_2#,
          # type = ifelse(input$log, "log", "linear")
        )
      )

  })
  
  output$timeseriesPlot_1 <- renderPlotly({

    filteredData <- copy(df_3) %>%
      filter(date == ymd(input$date)) %>%
      select(datetime, input$variable, wind_sensor_unit) %>%
  setorder(datetime) %>% drop_na(c(input$variable)) 
    

    plot_ly(
      filteredData,
      x = ~ datetime,
      y = ~ get(input$variable),
      color = ~ paste("Station", wind_sensor_unit),
      # type = 'scatter',
      mode = 'lines+markers'
    ) %>%
      layout(
        title = NULL,
        xaxis = list(title = 'Time'),
        yaxis = list(
          title = input$variable#,
          # type = ifelse(input$log, "log", "linear")
        )
      )

  })
}
# Run the app
shinyApp(ui = ui, server = server, options = list(height = 1200) )
```




# General conditions

```{r echo=FALSE, message=FALSE, warning=FALSE}
cond_general_scenario[, note := iconv(note, to = "utf-8")]
cond_general_scenario  %>%
  datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))# %>% formatDate(c("start_datetime","end_datetime"), method = "toLocaleString")
```

## Innova conditions

```{r echo=FALSE, message=FALSE, warning=FALSE}
    cond_innova_vc %>%
  datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

## Source and receptor conditions

```{r echo=FALSE, message=FALSE, warning=FALSE}
    cond_source_and_receptor%>%
  datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

## Wind sensor conditions

```{r echo=FALSE, message=FALSE, warning=FALSE}
    cond_wind_sensor %>%
  datatable( rownames = FALSE, filter = "top", extensions = 'Buttons', editable = TRUE, options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```



